### 2022-04-25 draft.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@30370e50710512481236934897d72d7fa51b0675 🚀
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@5b50cf18b0fa9d8ad7dc7964cb106d172f6d46ca 🚀

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}\quad %
Peregrin\,Took%
%
\,\textsuperscript{3,4}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Inn of the Prancing
Pony\quad \textsuperscript{4}\,Fellowship of the
Ring\quad \textsuperscript{5}\,Green Dragon Inn

@@

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

@@

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

@@

\newpage
\begin{landscape}

@@

\end{landscape}

>>>>

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Trophic resources of the edaphic
microarthropods: a worldwide review of the empirical evidence}
\vskip 5em

%
Víctor Nicolás\,Velazco%
%
\,\textsuperscript{1,2,‡}\quad %
Leonardo Ariel\,Saravia%
%
\,\textsuperscript{3,4,‡}

\textsuperscript{1}\,Departamento de Ciencias
Básicas\quad \textsuperscript{2}\,Universidad Nacional de Luján
(Argentina)\quad \textsuperscript{3}\,Instituto de Ciencias, Universidad
Nacional de General Sarmiento
(Argentina)\quad \textsuperscript{4}\,Centro Austral de Investigaciones
Científicas (CADIC-CONICET), Ushuaia, Argentina.

@@

\textbf{Correspondance to:}\\
Víctor Nicolás Velazco --- \texttt{}\\
Leonardo Ariel Saravia --- \texttt{lsaravia@campus.ungs.edu.ar}\\

@@

        {\bfseries Abstract:}\,Ecosystem sustainable use requires
reliable information about its biotic and abiotic structure and
functioning. Accurate knowledge of trophic relations is central for the
understanding of ecosystem dynamics, which in turn, is essential for
food web stability analyzes and the development of sustainable
practices. There is a rapid growth in the knowledge on how belowground
biodiversity regulates the structure and functioning of terrestrial
ecosystems. Although, the available information about trophic
relationships is hard to find and fragmented. This gathering the
information available worldwide about the food resources of soil
mesofauna. From the 3105 hits of the initial search on food resources of
soil microarthropods, only a total of 195 published works related
particular species, genera, and families to particular trophic
resources, the majority of them dealing with soils of the Palearctic
region. From the 195 publications we extracted 3009 records relating
specific taxonomic groups to their trophic resources, 20\% mention
saprophytic fungi as a food resource, 16\% cite microfauna, 11\% mention
bacteria, 10\% litter and 5\% cite Mycorrhizal fungi. The available
information was highly skewed, the 73.71\% comes from Acari, and within
these, 50.62\% correspond just to Sarcoptiformes. For Collembola, the
literature is scarce, the majority coming from Arthropleona. This review
highlights the general lack of information relating species, genera, and
families of the soil mesofauna to specific trophic resources. It also
highlights that available research mostly comes from European sites,
with the use of trophic resources by the mesofauna of the majority of
the soils in other parts of the world still largely unknown.\\%

@@

\newpage
\blandscape

@@

\elandscape

### 2022-04-25 preprint.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@30370e50710512481236934897d72d7fa51b0675 🚀
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@5b50cf18b0fa9d8ad7dc7964cb106d172f6d46ca 🚀

\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
manuscripts using markdown and github actions}}}

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}, %
Peregrin\,Took%
%
\,\textsuperscript{3,4}, %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}
\vskip 1em
\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
Prancing Pony; \textsuperscript{4}\,Fellowship of the
Ring; \textsuperscript{5}\,Green Dragon Inn\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

@@

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
pandoc\\pandoc-crossref\\github actions\\}
}

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

>>>>

\noindent {\LARGE \textbf{\textsf{Trophic resources of the edaphic
microarthropods: a worldwide review of the empirical evidence}}}

\medskip
\begin{flushleft}
{\small
%
Víctor Nicolás\,Velazco%
%
\,\textsuperscript{1,2,‡}, %
Leonardo Ariel\,Saravia%
%
\,\textsuperscript{3,4,‡}
\vskip 1em
\textsuperscript{1}\,Departamento de Ciencias
Básicas; \textsuperscript{2}\,Universidad Nacional de Luján
(Argentina); \textsuperscript{3}\,Instituto de Ciencias, Universidad
Nacional de General Sarmiento (Argentina); \textsuperscript{4}\,Centro
Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia,
Argentina.\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Víctor Nicolás Velazco --- \texttt{}\\
Leonardo Ariel Saravia --- \texttt{lsaravia@campus.ungs.edu.ar}\\
}
\end{flushleft}

@@

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
trophic ecology\\soil mesofauna\\Acari\\Collembola\\}
}

        {\bfseries Abstract:}\,Ecosystem sustainable use requires
reliable information about its biotic and abiotic structure and
functioning. Accurate knowledge of trophic relations is central for the
understanding of ecosystem dynamics, which in turn, is essential for
food web stability analyzes and the development of sustainable
practices. There is a rapid growth in the knowledge on how belowground
biodiversity regulates the structure and functioning of terrestrial
ecosystems. Although, the available information about trophic
relationships is hard to find and fragmented. This gathering the
information available worldwide about the food resources of soil
mesofauna. From the 3105 hits of the initial search on food resources of
soil microarthropods, only a total of 195 published works related
particular species, genera, and families to particular trophic
resources, the majority of them dealing with soils of the Palearctic
region. From the 195 publications we extracted 3009 records relating
specific taxonomic groups to their trophic resources, 20\% mention
saprophytic fungi as a food resource, 16\% cite microfauna, 11\% mention
bacteria, 10\% litter and 5\% cite Mycorrhizal fungi. The available
information was highly skewed, the 73.71\% comes from Acari, and within
these, 50.62\% correspond just to Sarcoptiformes. For Collembola, the
literature is scarce, the majority coming from Arthropleona. This review
highlights the general lack of information relating species, genera, and
families of the soil mesofauna to specific trophic resources. It also
highlights that available research mostly comes from European sites,
with the use of trophic resources by the mesofauna of the majority of
the soils in other parts of the world still largely unknown.\\%
